The Calculus of Linear Constructions

### 2021-10-16 writing/draft3.tex
draft

\renewcommand{\syntleft}{}
\renewcommand{\syntright}{}
\setlength{\grammarparsep}{10pt}
\setlength{\grammarindent}{10em}
\newcommand{\indalt}[1][2]{\\\hspace*{-1.2em}\textbar\quad}
\newcommand{\rname}[1]{\textsc{\footnotesize #1}}
\newcommand{\LNLD}{\text{LNL}_\text{D}}
\newcommand{\ok}{\textbf{ok}}
\newcommand{\pure}[1]{|#1|}
\newcommand{\sort}{\textbf{sort}}
\newcommand{\type}{\textbf{type}}
\newcommand{\refl}{\text{refl}}
\newcommand{\letin}[3]{$\text{let }#1\text{ := }#2\text{ in }#3$}
\newcommand{\new}{\text{new}}
\newcommand{\free}{\text{free}}
\newcommand{\get}{\text{get}}
\newcommand{\set}{\text{set}}
\newcommand{\subst}{\text{subst}}
\newcommand{\utype}{:_{\scriptscriptstyle U}}
\newcommand{\ltype}{:_{\scriptscriptstyle L}}
\newcommand{\stype}[1]{:_#1}
\newcommand{\step}{\leadsto}
\newcommand{\pstep}{\leadsto}
\newcommand{\mrg}[3]{#1\ddagger#2\ddagger#3}
\newcommand{\arw}[2]
{\hspace*{0.2em}{\scriptstyle #1}\hspace*{-0.2em}
\rightarrow
\hspace*{-0.2em}{\scriptstyle #2}\hspace*{0.2em}}
\newcommand{\lrw}[2]
{\hspace*{0.2em}{\scriptstyle #1}\hspace*{-0.2em}
\multimap
\hspace*{-0.2em}{\scriptstyle #2}\hspace*{0.2em}}
\newcommand{\erase}[1]{\llbracket #1 \rrbracket}

@@

  \subsubsection{Promotion and Dereliction}
  In most presentations of linear logic, there is no clear distinction between linear and non-linear objects. Non-linear objects are created by packing linear objects under non-linear contexts into the ! exponential through the \textit{promotion} rule. Conversely, the \textit{dereliction} rule unpacks ! objects so they can be used in place of linear ones. Linear type theories \cite{abramsky1993,dill,vakar14} based on ! will contain introduction and elimination rules for ! types that serve similar purpose to \textit{promotion} and \textit{dereliction}.

  The linear types of CLC are not designed around packing and unpacking !, so there are no explicit rules for \textit{promotion} and \textit{dereliction}. However, \textit{promotion} and \textit{dereliction} for canonical types are derivable as theorems through $\eta$-expansion.

@@

  For the following theorem, we refer to the reductions in CLC as $\pstep_{\scriptscriptstyle \text{CLC}}$, and the reductions in CC$\omega$ as $\pstep_{\scriptscriptstyle \text{CC$\omega$}}$.
  \begin{theorem} \label{preserve} Erasure preserves reduction. \\
    For any CLC terms $m$, and $n$, if there is $m \pstep_{\scriptscriptstyle \text{CLC}} n$, then there is $\erase{m} \pstep_{\scriptscriptstyle \text{CC$\omega$}} \erase{n}$.
  \end{theorem}

  \begin{theorem} \label{embedding} Embedding. \\
    If $\Gamma \vdash m \stype{s} A$ is a valid judgment in CLC, then $\erase{\Gamma} \vdash \erase{m} : \erase{A}$ is a valid judgment in CC$\omega$.
  \end{theorem}

  If there exists some well typed CLC term with an infinite sequence of reductions, erasure will embed this term into a well typed CC$\omega$ term along with its infinite sequence of reductions by virtue of theorems \ref{preserve}, and \ref{embedding}. This is contradictory to the strong normalization property of CC$\omega$ proven through the Girard-Tait method \cite{ecc}, so this hypothetical term does not exist in CLC.

>>>>

\renewcommand{\syntleft}{}
\renewcommand{\syntright}{}
\setlength{\grammarparsep}{10pt}
\setlength{\grammarindent}{10em}
\newcommand{\indalt}[1][2]{\\\hspace*{-1.2em}\textbar\quad}
\newcommand{\rname}[1]{\textsc{\footnotesize #1}}
\newcommand{\LNLD}{\text{LNL}_\text{D}}
\newcommand{\ok}{\textbf{ok}}
\newcommand{\pure}[1]{|#1|}
\newcommand{\sort}{\textbf{sort}}
\newcommand{\type}{\textbf{type}}
\newcommand{\refl}{\text{refl}}
\newcommand{\letin}[3]{$\text{let }#1\text{ := }#2\text{ in }#3$}
\newcommand{\new}{\text{new}}
\newcommand{\free}{\text{free}}
\newcommand{\get}{\text{get}}
\newcommand{\set}{\text{set}}
\newcommand{\subst}{\text{subst}}
\newcommand{\utype}{:_{\scriptscriptstyle U}}
\newcommand{\ltype}{:_{\scriptscriptstyle L}}
\newcommand{\stype}[1]{:_#1}
\newcommand{\step}{\leadsto}
\newcommand{\pstep}{\leadsto}
\newcommand{\mrg}[3]{#1\ddagger#2\ddagger#3}
\newcommand{\erase}[1]{\llbracket #1 \rrbracket}

@@

  \subsubsection{Promotion and Dereliction}
  In most presentations of linear logic, non-linear objects are created by packing linear objects under non-linear contexts into the ! exponential through the \textit{promotion} rule. Conversely, the \textit{dereliction} rule unpacks non-linear objects so they can be used in place of linear ones. Linear type theories \cite{abramsky1993,dill,vakar14} utilizing exponential for non-linearity will contain ! types and rules that are equivalent to \textit{promotion} and \textit{dereliction}.

  Linear types of CLC are not designed around packing and unpacking !, so there are no rules for \textit{promotion} and \textit{dereliction}. Arbitrary computations existing at the type level also muddle the association between which types can be promoted or derelicted to which. Nevertheless, \textit{promotion} and \textit{dereliction} for canonical types are derivable as theorems through $\eta$-expansion.

@@

  For the following lemma, we refer to the reductions in CLC as $\pstep_{\scriptscriptstyle \text{CLC}}$, and the reductions in CC$\omega$ as $\pstep_{\scriptscriptstyle \text{CC$\omega$}}$.
  \begin{lemma} \label{preserve} Erasure preserves reduction. \\
    For any CLC terms $m$, and $n$, if there is $m \pstep_{\scriptscriptstyle \text{CLC}} n$, then there is $\erase{m} \pstep_{\scriptscriptstyle \text{CC$\omega$}} \erase{n}$.
  \end{lemma}

  \begin{lemma} \label{embedding} Embedding. \\
    If $\Gamma \vdash m \stype{s} A$ is a valid judgment in CLC, then $\erase{\Gamma} \vdash \erase{m} : \erase{A}$ is a valid judgment in CC$\omega$.
  \end{lemma}

  If there exists some well typed CLC term with an infinite sequence of reductions, erasure will embed this term into a well typed CC$\omega$ term along with its infinite sequence of reductions by virtue of lemmas \ref{preserve}, and \ref{embedding}. This is contradictory to the strong normalization property of CC$\omega$ proven through the Girard-Tait method \cite{ecc}, so this hypothetical term does not exist in CLC.
